---
title: "Demo"
author: "Richèl J.C. Bilderbeek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(daisieme)
```

Setup up the parameters:

```{r}
dme_params_filename <- tempfile()
ana_psr <- 1.23
clado_is_psr <- 2.34
clado_main_psr <- 3.45
ext_is_psr <- 0.12
ext_main_psr <- 0.23
mig_to_is_psr <- 0.001
carry_cap_is <- 42
carry_cap_main <- 314
rng_seed <- 421
init_n_main_clades <- 1
init_n_main_sps <- 9
crown_age <- 1.23
daisie_sim_results_filename <- tempfile()
daisie_input_ideal_filename <- tempfile()
daisie_input_reality_filename <- tempfile()
daisie_output_ideal_filename <- ""
daisie_output_reality_filename <- ""
```

If you want to let DAISIE estimate the parameter values, set
the following to `TRUE`:

```{r}
run_daisie <- FALSE
if (run_daisie) {
  daisie_output_ideal_filename <- tempfile()
  daisie_output_reality_filename <- tempfile()
}
```

Here we run a simulation with mainland extinction:

```{r}
dme_sim(
  ana_psr = ana_psr,
  clado_is_psr = clado_is_psr,
  clado_main_psr = clado_main_psr,
  ext_is_psr = ext_is_psr,
  ext_main_psr = ext_main_psr,
  mig_to_is_psr = mig_to_is_psr,
  carry_cap_is = carry_cap_is,
  carry_cap_main = carry_cap_main,
  rng_seed = rng_seed,
  init_n_main_clades = init_n_main_clades,
  init_n_main_sps = init_n_main_sps,
  crown_age = crown_age,
  dme_params_filename = dme_params_filename,
  daisie_sim_results_filename = daisie_sim_results_filename,
  daisie_input_ideal_filename = daisie_input_ideal_filename,
  daisie_input_reality_filename = daisie_input_reality_filename,
  daisie_output_ideal_filename = daisie_output_ideal_filename,
  daisie_output_reality_filename = daisie_output_reality_filename
)
```

daisieme parameters:

```{r}
cat(dme_params_filename)
```

daisieme sim results:

```{r}
readLines(daisie_sim_results_filename)
```

DAISIE input for ideal scenario (can be close to empty if
nothing interesting happens):

```{r}
readLines(daisie_input_ideal_filename)
```

DAISIE input for realistic scenario (can be close to empty if
nothing interesting happens):

```{r}
readLines(daisie_input_reality_filename)
```

DAISIE parameter estimates (if run)

```{r}
if (run_daisie) {
  readLines(daisie_output_ideal_filename)
}
```

DAISIE parameter estimates (if run) in reality

```{r}
if (run_daisie) {
  readLines(daisie_output_reality_filename)
}
```
